\IEEEPARstart{M}{ulti-objective} Evolutionary Algorithms (\MOEAS{}) are one of the most popular approaches 
to deal with Multi-objective Optimization Problems (\MOPS{})~\cite{das2011real, zhou2011multiobjective}.
%
\MOEAS{} are usually employed in complex problems where more traditional optimization techniques are not 
applicable~\cite{Lootsma:99}.
%
%TODO: tal y como lo defines no es box-constrained. Quita lo de box-constrained o mejor define las restricciones
%de caja.
A continuous box-constrained minimization \MOP{}, which is the case addressed in this paper,
involves two or more conflicting objectives as defined in (\ref{eqn:main})
%
\begin{equation}\label{eqn:main}
\begin{split}
&min \quad F(x) = (f_1(x), ..., f_M(x)) \\
&s.t. \quad x_i^{(L)} \leq x_i \leq x_i^{(U)}
%&s.t. \quad x \in \Omega.
\end{split}
\end{equation}

where $x \in \Re^D$, $D$ is the number of variables,
and each decision variable $x_i \in \Re$ is constrained by $x_i^{(L)}$ and $x_i^{(U)}$, 
i.e. the lower bound and the upper bound.
%$\Omega \subseteq \Re^D$ denotes the decision or variable space, 
The feasible space bounded by $x_i^{(L)}$ and $x_i^{(U)}$ is denoted by $\Omega$.
Each solution is mapped to the \textit{objective space} $Y$ with the function $F: \Omega \rightarrow Y \subseteq \Re^M$, 
which consists of $M$ real-valued objective functions.
%
%
%Decidir quitar estas definiciones porque la introduccion está muy larga
%
%Given two solutions $x_1, x_2 \in \Omega$, $x_1$ dominates $x_2$, denoted as $x_1 \prec x_2$, 
%if and only if $f_i(x_1) \leq f_i(x_2)\ \forall\  i \in \{1,...,M\}$ and 
%$\exists i \in \{1,...,M\}: \ f_i(x_1) < f_i(x_2)$.
%
%A solution $x^*$ is a Pareto-optimal solution if $\not \exists x \in \Omega : x \prec x^*$.
%
%The set of Pareto-optimal solutions is called the Pareto-optimal set (\PS{}), and their images are the 
%Pareto Front (\PF{}).
%
The goal of most \MOEAS{} is to find a proper approximation of the Pareto Front, i.e., a set of
solutions whose images are well-distributed and close to the Pareto Front~\cite{trivedi2016survey}.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% end paragraph

%Evolutionary Algorithms (\EAS{}) are one of the most popular meta-heuristics employed to tackle 
%\MOPS{}.
%
In recent years, the development of \MOEAS{} has grown dramatically~\cite{van1998multiobjective, coello2007mop}, resulting 
in effective and broadly applicable algorithms.
%
However, some function features provoke significant degradation on the performance of \MOEAS{}~\cite{huband2006review}, 
so better design principles are yet required.
%
%TODO: Citar tras taxonomies alguna clasificacion, preferiblemente la de decomposition, dominance, quality.
Regarding the design of \MOEAS{}, several paths have been explored resulting in diverse taxonomies~\cite{trivedi2016survey}.
%
For instance, principles related to decomposition, dominance and quality metrics are used
to design \MOEAS{}.
%
Current state-of-the-art \MOEAS{} consider in some way the diversity on the objective space.
%
In some cases, this is done explicitly through density estimators~\cite{beume2007sms}, %TODO: Citar algun density estimator
whereas in other cases,
%such as in decomposition-based methods 
this is done indirectly~\cite{zhang2007moea}. 
%with the use of a diverse set of weights. %TODO: Citar MOEA/D
%
Since optimizing most objective space quality indicators implies attaining a well-spread set of solutions in the
objective space, not considering this kind of diversity would result in quite ineffective optimizers.
%
A quite different condition appears with respect to diversity on the variable space.
%
Since objective space quality metrics do not consider at all the diversity on the variable space,
most \MOEAS{} designers disregard this diversity.

Differently, %when looking at the best optimizers for other areas of optimization, such as i
%the single-objective case,
%it is clear that 
several state-of-the-art single-objective methods introduce mechanisms to vary the trend of the 
diversity on the variable space even if obtaining a diverse
set of solutions is not the aim of the optimization~\cite{Joel:Crepinsek}.
%
Instead, this is done to induce a better balance between exploration and exploitation.
%
In fact, the proper management of diversity is considered as one of the cornerstones for proper performance~\cite{Herrera-Poyatos:17}.
%
Thus, these differences between the design principles applied in single-objective and multi-objective evolutionary 
algorithms are shocking.
%
Moreover, practitioners have shown that modern \MOEAS{} suffer some drawbacks related to stagnation and premature 
convergence in subset of variables~\cite{ishibuchi2006comparison, castillo2017multi, buche2003self, lu2002dynamic}.
%
As a result, this paper studies the hypothesis that incorporating mechanisms to manage the diversity on the decision space 
might bring important benefits to the field of multi-objective optimization.
%
%TODO: citar ejemplos significativos de niching-based MOEAS{}.
Note that differently to other proposals, such as niching-based \MOEAS{}~\cite{mahfoud1995niching, srinivas1994muiltiobjective}, we are not interested in obtaining
a diverse set of solutions in the decision space.
%
Instead, we state that the quality of the results in terms of objective-space indicators can be improved further with these
kinds of mechanisms.

Since controlling diversity to attain a proper balance between exploration and intensification have been considered 
so important in single-objective domains~\cite{lin2009auto},
quite a large amount of related methods have been devised~\cite{Joel:Crepinsek}. 
%
%Esto esta interesante, pero muy largo, lo pasare a la parte de literatura
%Note that in most cases, similar principles have been used to devise niching methods that try to locate
%several optima simultaneously and methods that try to properly balance exploration and intesification but with the aim
%of attaining a single optimum.
%
%However, since the aim is quite different, methods that are specific to one of these areas
%have also been proposed.
%
%The applied principles to vary the way diversity evolves are quite assorted so several taxonomies have been proposed.
%
%They are classified in~\cite{Joel:Crepinsek} in terms of the involved component that is altered.
%
%Some of the most prominent categories that are identified are the following: 
%selection-based~\cite{Chen:09}, 
%population-based\cite{koumousis2006saw}, 
%crossover/mutation-based~\cite{herrera2003fuzzy}, %mitchell1998introduction
%fitness-based~\cite{Cioppa:07}, 
%and replacement-based~\cite{segura2015novel}.
%
Recent research in single-objective optimization has shown that important advances are attained when the
balance between exploration and intensification is managed by relating the amount of maintained population's diversity to 
the stopping criterion and elapsed period of execution.
%
Particularly, these methods reduce the importance given to the preservation of diversity as the end of the optimization
is approached.
%
This principle has been used to find new best-known solutions for the Frequency Assignment Problem 
(FAP)~\cite{segura2016improving}, to improve further continuous optimizers~\cite{castillo2019differential} and
to design the winning strategy of the extended round of Google Hash Code 
2020\footnote{https://codingcompetitions.withgoogle.com/hashcode/}, with more than $100,000$ participants.
%
Thus, we decided to explore the incorporation of this principle in the design of \MOEAS{}.
%
%Probably, one of the most important drawbacks of this design principle is that most discussed optimizers require long-term
%executions to excel.
%
%Even if this is the case for \MOEAS{}, there is a niche for these kinds of optimizers, so exploring them is important.
%Toda la parte de detalles de Evolución Diferencial se me hacían demasiado largas, tal vez para la revisión de literatura sí
%está bien.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% end paragraph

One of the main difficulties for incorporating the previous principle to the design of \MOEAS{} is that
meassures of the variable space and objective space must be taken into account simultaneously.
%and the relation between them is problem-dependent.
%
The discussed design principle is based on reducing the importance of diversity on variable space as 
generations evolve, so we maintain this decision and indirectly increase the importance granted to diversity 
and quality on objective space as the execution progresses.
%
%Esta es demasiado detalle asi que mejor para la propuesta
%In fact, our proposal behaves as a traditional \MOEA{} during the last half of the optimization, in the sense
%that the diversity on the variable space is disregarded.
%
In order to show the validity of our hypothesis, this paper proposes the
\textit{Archived Variable Space Diversity MOEA based on Decomposition} (\AVSDMOEAD{}).
%, which explicitly manage the diversity in the 
%variable space to properly balance from exploration towards intensification.
%
\AVSDMOEAD{} simplifies \MOEADDE{}~\cite{zhang2009performance} by deactivating the dynamical resource allocation
scheme and the notion of neighborhood,
%Lo de panmictic lo pasamos a la propuesta, para acortar aqui
%, meaning that the more traditiona panmictic population is used, 
and at the same
time extends it by including a novel replacement strategy that applies the discussed design principles.
%
Validation of our proposal is carried out taking into consideration 
\MOEADDE{}~\cite{zhang2009performance}, 
\NSGAII{}~\cite{deb2002fast}, 
\REMOA{}~\cite{trautmann2013r2} and 
\NSGAIII{}~\cite{deb2013evolutionary}.
%Esto lo pasamos para la validación con el fin de acortar
%which are popular representatives of decomposition-based, dominance-based, indicator-based and hybrid \MOEAS{}, respectively.
%
Remarkable benefits are attained in terms of robustness and scalability.

The rest of this paper is organized as follows.
%
Section~\ref{Sec:LiteratureReview} provides a review of \MOEAS{}, diversity management 
and some other related works.
%
The \AVSDMOEAD{} proposal is detailed in section~\ref{Sec:Proposal}.
%
Section~\ref{Sec:ExperimentalValidation} is devoted to an extensive experimental validation of the novel proposal and
design principle.
%
Finally, conclusions and some lines of future work are given in section~\ref{Sec:Conclusion}.
%
